---
title: "HW 5 for P8105 - hlz2108"
author: "Helen Zhang"
date: "November 10, 2020"
output: github_document
---
Below is the code for setup:

```{r setup}
library(tidyverse)
library(dplyr)
library(readxl)
library(ggplot2)
library(p8105.datasets)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 0

This “problem” focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files.

## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsovled ...
  n_total ... 
  
  prop.test(.....)
  
}
homicide_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```

## Problem 2

Importing and tidying data files.

```{r data_files_tidy}
data_files = 
  tibble(
    path = list.files(path = "./lda_data", full.names = FALSE)
) %>%
  mutate(
    data = map(.x = str_c("./lda_data/", path), ~ read_csv(.x))) %>% 
  unnest(data) %>%
  separate(path, into = c("arm", "subject_id", "csv")) %>%
  select(-csv) %>% 
  pivot_longer(
    cols = week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation"
  ) %>% 
  mutate(
    arm = recode(arm, "con" = "Control", "exp" = "Experimental")) 

data_files
```

Making the spaghetti_plot!

```{r spaghetti_plot}
plot_data = data_files %>% 
  ggplot(aes(x = week, y = observation, group = subject_id, color = subject_id)) + 
  geom_point(alpha = 0.5) +
  geom_line() +
  facet_grid( ~ arm) +
  labs(
    title = "Observations over Time by Subject",
    x = "Week",
    y = "Observation"
  ) + 
  theme(plot.title = element_text(hjust = 0.5))
  
plot_data
```

At week 1, observation values were slightly higher in the experimental group than the control group. 
The experimental group had increasing observation values across the study period from week 1 to week 8. The experimental group had higher observation values than the control group.Meanwhile, the control group appeared to be relatively stagnant, with some participants having decreased values at week 8 as compared to week 1.
Overall, the control group had lower observation values compared to the experimental group.

## Problem 3

```{r sim_function}
set.seed(222)
t_test = function(samp_size, mu = 0, sigma = 5){
  
  sim_data = 
    tibble(
      x = rnorm(n = samp_size, mean = mu, sd = sigma)
    )
  
  sim_data %>%
  t.test(mu = 0, conf.level = 0.95) %>%
  broom::tidy() %>% 
  select(estimate, p.value)
}
```

```{r sim_results}
sim_results =
  rerun(5000, t_test(samp_size = 30)) %>% 
  bind_rows() %>% 
  view
```

```{r sim_results_2}
sim_results_2 =
  tibble(
    mu = c(0,1,2,3,4,5,6)
  ) %>% 
  mutate(
    output_lists = map(.x = mu, ~ rerun(5000, t_test(30, mu = .x))),
    estimate_df = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists) %>% 
  unnest(estimate_df)

sim_results_2
```

Let's make a plot.

```{r power_plot}
results_df =
sim_results_2 %>% 
  group_by(mu) %>% 
  mutate(
    result = case_when(
      p.value < 0.05 ~ "reject",
      p.value > 0.05 ~"fail to reject"
      )
    )
    
power_plot = results_df %>% 
  group_by(mu) %>% 
  summarise(
    sum = sum(p.value < 0.05),
    count = n(),
    rej_proportion = sum/count) %>% 
  ggplot(aes(x = mu, y = rej_proportion)) + 
  geom_point() +
  geom_line() +
  labs(
    title = "Association between Effect Size and Power",
    x = "True μ Value",
    y = "Proportion of Times Null was Rejected (Power)"
  ) + 
  theme(plot.title = element_text(hjust = 0.5))

power_plot
```

From the plot, it appears that as effect size increases, power also increases.

```{r total_p}
total_p =
  results_df %>% 
  group_by(mu) %>%
  summarize(
    avg_mu = mean(estimate)
  ) %>% 
  ggplot(aes(x = mu, y = avg_mu)) + 
  geom_point() +
  geom_line() +
  labs(
    title = "Total Samples",
    x = "True μ Value",
    y = "Average Estimate of μ"
  ) + 
  theme(plot.title = element_text(hjust = 0.5))

total_p
```

```{r rejects_p}
rejects_p =
  results_df %>% 
  group_by(mu) %>%
  filter(result == "reject") %>% 
  summarise(
    avg_mu = mean(estimate)
  ) %>% 
  ggplot(aes(x = mu, y = avg_mu)) + 
  geom_point() +
  geom_line() +
  labs(
    title = "Rejected Samples",
    x = "True μ Value",
    y = "Average Estimate of μ"
  ) + 
  theme(plot.title = element_text(hjust = 0.5))

rejects_p
```

```{r patchwork_p}
total_p + rejects_p
```

In the plot with all samples, the true mean is approximately equal to the average estimate. However, in the plot with only samples for which the null was rejected, the average estimate only approximates the true mean when the effect size is between 4 and 6. This indicates that when effect size is large, the average estimate is a good approximation of the true value. When effect size is small, between 0-3, we can see that the average estimate is not a good approximate for the true value. The plot suggests that when the effect size is small, it is possible that the average estimate would overestimate the true mean.
