---
title: "HW 5 for P8105 - hlz2108"
author: "Helen Zhang"
date: "November 10, 2020"
output: github_document
---
Below is the code for setup:

```{r setup}
library(tidyverse)
library(dplyr)
library(readxl)
library(ggplot2)
library(p8105.datasets)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 0

This “problem” focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files.

## Problem 1

```{r homicide_df}
homicide_df =
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved", 
      disposition == "Open/No arrest"        ~ "unsolved", 
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```


Let's look at this a bit

```{r aggregate_df}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarise(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  ) %>% view
```

Can I do a prop test for a single city?

```{r prop_tests}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate...

```{r results_df}
results_df =  
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>%
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>%
  select(city_state, estimate, conf.low, conf.high)
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsolved...
  n_total...
  
  prop.test(...)
  
}
```

## Problem 2

```{r}
data_1 = read_csv("lda_data/con_01.csv")
```


```{r}
path_df = 
  tibble(
    path = list.files("lda_data"),
) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map(.....))

read_csv(path_df$path[[1]])
```

This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

## Problem 3
When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a simple linear regression.

First set the following design elements:

Fix n=30
Fix σ=5
Set μ=0. Generate 5000 datasets from the model

x∼Normal[μ,σ]

For each dataset, save μ̂  and the p-value arising from a test of H:μ=0 using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.

Repeat the above for μ={1,2,3,4,5,6}, and complete the following:

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
Make a plot showing the average estimate of μ̂  on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ̂  only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ̂  across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?
